### 2021-03-23 input/figproofB.tex
issue depiction

  \draw[<->] (-5pt - \X, -\Y) -- node[above]{III} (5pt, -\Y); %% III    
  \draw[->] (-\X + 5pt, 0) -- node[above, font=\small, color=\PC]{$\DEL_d$} (0 - 5pt, 0); %% d - e

  \draw[<->] (-5pt , 5pt -\Y) -- node[above]{IV} (5pt + \X, 5pt -\Y); %% IV
  \draw[->] (0 +5pt, 0) -- (\X -5pt, 0); %% e - b'

  \draw[<->] (-5pt + \X , 10pt -\Y) -- node[above]{V} (5pt + 2*\X, 10pt -\Y); %% V
  \draw[->] ( \X +5pt, 0) -- (2*\X -5pt, 0); %% b - b''

@@

  \draw ( 0, 5pt) node[above, color=\WRONG]{$\ADD_f^{0.5}$};
  \draw ( 0, -5pt) node[below, font=\footnotesize]{expect $\textcolor{\PB}{\DEL_f}$};

>>>>

  \draw[<->] (-5pt - \X, -\Y) -- node[above]{I} (5pt, -\Y); %% I as well
  \draw[->] (-\X + 5pt, 0) -- node[above, font=\small, color=\PC]{$\DEL_d$} (0 - 5pt, 0); %% d - e

  \draw[<->] (-5pt , 5pt -\Y) -- node[above]{III} (5pt + \X, 5pt -\Y); %% IV
  \draw[->] (0 +5pt, 0) -- (\X -5pt, 0); %% e - b'

  \draw[<->] (-5pt + \X , 10pt -\Y) -- node[above]{IV} (5pt + 2*\X, 10pt -\Y); %% V
  \draw[->] ( \X +5pt, 0) -- (2*\X -5pt, 0); %% b - b''

@@

  \draw ( 0, 5pt) node[above]{$\textcolor{\PC}{\ADD_d} \rightarrow \textcolor{\WRONG}{\ADD_f^{0.5}}$};
  \draw ( 0, -5pt) node[below, font=\footnotesize]{expect $\textcolor{\PB}{\DEL_f}$};

### 2021-03-23 input/proposal.tex
issue depiction

>>>>

Figure~\ref{fig:proof} depicts the issues with staleness and message
orderings. In Figure~\ref{fig:proofA}, the shortest path from any
source to Process $c$ is $[a, b, c]$. However, Process $b$ still holds
a stale $\alpha_d^{0.5}$ without knowing. When it receives
$\alpha_a^1$, it discards it, for it assumes that downstream processes
are more interested in $\alpha_d^{0.5}$. To reach consistent
partitioning, Process $b$ first needs to purge its current partition
to later accept that of its current actual shortest path:
$\alpha_a^1$.

\noindent Figure~\ref{fig:proofB} shows that removing stale control
information is even more complex. The removal must reach all processes
of the previous shortest path going from $d$ to $b''$. Label I shows
the most obvious issue where Process $e$ changed partition for a
better but stale $\alpha_f$. Since it can remember its previous
deliveries, it could still forward $\delta_d$ for the sake of
consistency. However, this would lead to every process forwarding
every $\delta$ they ever delivered. Such protocol's overhead would
depend on past partitioning instead of current one. Label III shows
the issue when the blocking partition is already known to be stale at
Process $b'$. Process $b''$ eventually receives $\alpha_f$ from
$e$. However, it cannot deliver it, for it would break last win order.
Process $b'$ may be in an inconsistent state. Label IV shows the
corollary issue: Process $b''$ delivered a message from a process that
may be inconsistent without knowing it.
